OECD Actuals and BVAR Specifications

### 2024-08-28 manuscript/manuscript.tex
old documentation (pre major manuscript)

\newpage
\begin{longtable}{l|rrr}
\toprule
\multicolumn{1}{l}{} & IMF & ar & bvar \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{4}{l}{horizon = 0} \\ 
\midrule\addlinespace[2.5pt]
expanding window\_interval\_score & 0.114 & 0.124 & 0.122 \\ 
expanding window\_sample\_crps & 0.087 & 0.093 & 0.092 \\ 
leave-one-out\_interval\_score & 0.110 & 0.122 & 0.121 \\ 
leave-one-out\_sample\_crps & 0.088 & 0.099 & 0.100 \\ 
rolling window\_interval\_score & 0.117 & 0.126 & 0.124 \\ 
rolling window\_sample\_crps & 0.090 & 0.093 & 0.092 \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{4}{l}{horizon = 0.5} \\ 
\midrule\addlinespace[2.5pt]
expanding window\_interval\_score & 0.255 & 0.280 & 0.305 \\ 
expanding window\_sample\_crps & 0.179 & 0.205 & 0.235 \\ 
leave-one-out\_interval\_score & 0.254 & 0.267 & 0.289 \\ 
leave-one-out\_sample\_crps & 0.180 & 0.217 & 0.230 \\ 
rolling window\_interval\_score & 0.256 & 0.272 & 0.292 \\ 
rolling window\_sample\_crps & 0.184 & 0.196 & 0.223 \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{4}{l}{horizon = 1} \\ 
\midrule\addlinespace[2.5pt]
expanding window\_interval\_score & 0.464 & 0.764 & 0.607 \\ 
expanding window\_sample\_crps & 0.344 & 0.547 & 0.448 \\ 
leave-one-out\_interval\_score & 0.456 & 0.776 & 0.600 \\ 
leave-one-out\_sample\_crps & 0.302 & 0.448 & 0.400 \\ 
rolling window\_interval\_score & 0.471 & 0.768 & 0.611 \\ 
rolling window\_sample\_crps & 0.347 & 0.550 & 0.452 \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{4}{l}{horizon = 1.5} \\ 
\midrule\addlinespace[2.5pt]
expanding window\_interval\_score & 0.517 & 1.043 & 0.807 \\ 
expanding window\_sample\_crps & 0.367 & 0.635 & 0.612 \\ 
leave-one-out\_interval\_score & 0.507 & 1.023 & 0.755 \\ 
leave-one-out\_sample\_crps & 0.337 & 0.583 & 0.577 \\ 
rolling window\_interval\_score & 0.521 & 1.042 & 0.787 \\ 
rolling window\_sample\_crps & 0.361 & 0.623 & 0.576 \\ 
\bottomrule
\end{longtable}

@@

\begin{longtable}{l|rrr}
\toprule
\multicolumn{1}{l}{} & IMF & ar & bvar \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{4}{l}{horizon = 0} \\ 
\midrule\addlinespace[2.5pt]
expanding window\_interval\_score & 0.229 & 0.295 & 0.291 \\ 
expanding window\_sample\_crps & 0.168 & 0.200 & 0.195 \\ 
leave-one-out\_interval\_score & 0.222 & 0.292 & 0.291 \\ 
leave-one-out\_sample\_crps & 0.183 & 0.219 & 0.214 \\ 
rolling window\_interval\_score & 0.232 & 0.292 & 0.287 \\ 
rolling window\_sample\_crps & 0.169 & 0.197 & 0.190 \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{4}{l}{horizon = 0.5} \\ 
\midrule\addlinespace[2.5pt]
expanding window\_interval\_score & 0.408 & 0.558 & 0.510 \\ 
expanding window\_sample\_crps & 0.289 & 0.390 & 0.370 \\ 
leave-one-out\_interval\_score & 0.396 & 0.550 & 0.500 \\ 
leave-one-out\_sample\_crps & 0.310 & 0.408 & 0.377 \\ 
rolling window\_interval\_score & 0.411 & 0.565 & 0.519 \\ 
rolling window\_sample\_crps & 0.290 & 0.402 & 0.374 \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{4}{l}{horizon = 1} \\ 
\midrule\addlinespace[2.5pt]
expanding window\_interval\_score & 0.878 & 1.176 & 1.018 \\ 
expanding window\_sample\_crps & 0.664 & 0.861 & 0.801 \\ 
leave-one-out\_interval\_score & 0.866 & 1.159 & 1.005 \\ 
leave-one-out\_sample\_crps & 0.634 & 0.759 & 0.709 \\ 
rolling window\_interval\_score & 0.901 & 1.201 & 1.044 \\ 
rolling window\_sample\_crps & 0.682 & 0.901 & 0.841 \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{4}{l}{horizon = 1.5} \\ 
\midrule\addlinespace[2.5pt]
expanding window\_interval\_score & 1.126 & 1.387 & 1.198 \\ 
expanding window\_sample\_crps & 0.841 & 0.977 & 0.956 \\ 
leave-one-out\_interval\_score & 1.097 & 1.381 & 1.195 \\ 
leave-one-out\_sample\_crps & 0.765 & 0.882 & 0.849 \\ 
rolling window\_interval\_score & 1.139 & 1.411 & 1.235 \\ 
rolling window\_sample\_crps & 0.864 & 1.022 & 1.005 \\ 
\bottomrule
\end{longtable}

>>>>

\newpage
\begin{longtable}{l|rrr}
\toprule
\multicolumn{1}{l}{} & IMF & ar & bvar \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{4}{l}{horizon = 0} \\ 
\midrule\addlinespace[2.5pt]
expanding window\_interval\_score & 0.142 & 0.088 & 0.078 \\ 
expanding window\_sample\_crps & 0.105 & 0.068 & 0.059 \\ 
leave-one-out\_interval\_score & 0.136 & 0.084 & 0.076 \\ 
leave-one-out\_sample\_crps & 0.107 & 0.049 & 0.046 \\ 
rolling window\_interval\_score & 0.141 & 0.087 & 0.078 \\ 
rolling window\_sample\_crps & 0.105 & 0.068 & 0.060 \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{4}{l}{horizon = 0.5} \\ 
\midrule\addlinespace[2.5pt]
expanding window\_interval\_score & 0.228 & 0.275 & 0.274 \\ 
expanding window\_sample\_crps & 0.164 & 0.190 & 0.210 \\ 
leave-one-out\_interval\_score & 0.228 & 0.268 & 0.263 \\ 
leave-one-out\_sample\_crps & 0.161 & 0.192 & 0.206 \\ 
rolling window\_interval\_score & 0.226 & 0.269 & 0.267 \\ 
rolling window\_sample\_crps & 0.166 & 0.183 & 0.204 \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{4}{l}{horizon = 1} \\ 
\midrule\addlinespace[2.5pt]
expanding window\_interval\_score & 0.420 & 0.757 & 0.595 \\ 
expanding window\_sample\_crps & 0.300 & 0.530 & 0.448 \\ 
leave-one-out\_interval\_score & 0.412 & 0.768 & 0.591 \\ 
leave-one-out\_sample\_crps & 0.272 & 0.440 & 0.388 \\ 
rolling window\_interval\_score & 0.420 & 0.765 & 0.600 \\ 
rolling window\_sample\_crps & 0.301 & 0.542 & 0.456 \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{4}{l}{horizon = 1.5} \\ 
\midrule\addlinespace[2.5pt]
expanding window\_interval\_score & 0.465 & 1.037 & 0.819 \\ 
expanding window\_sample\_crps & 0.323 & 0.603 & 0.613 \\ 
leave-one-out\_interval\_score & 0.456 & 1.013 & 0.765 \\ 
leave-one-out\_sample\_crps & 0.312 & 0.567 & 0.566 \\ 
rolling window\_interval\_score & 0.463 & 1.039 & 0.799 \\ 
rolling window\_sample\_crps & 0.319 & 0.604 & 0.582 \\ 
\bottomrule
\end{longtable}

@@

\begin{longtable}{l|rrr}
\toprule
\multicolumn{1}{l}{} & IMF & ar & bvar \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{4}{l}{horizon = 0} \\ 
\midrule\addlinespace[2.5pt]
expanding window\_interval\_score & 0.365 & 0.110 & 0.099 \\ 
expanding window\_sample\_crps & 0.254 & 0.083 & 0.076 \\ 
leave-one-out\_interval\_score & 0.356 & 0.112 & 0.099 \\ 
leave-one-out\_sample\_crps & 0.269 & 0.077 & 0.068 \\ 
rolling window\_interval\_score & 0.368 & 0.112 & 0.100 \\ 
rolling window\_sample\_crps & 0.267 & 0.086 & 0.079 \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{4}{l}{horizon = 0.5} \\ 
\midrule\addlinespace[2.5pt]
expanding window\_interval\_score & 0.446 & 0.506 & 0.455 \\ 
expanding window\_sample\_crps & 0.324 & 0.369 & 0.329 \\ 
leave-one-out\_interval\_score & 0.435 & 0.512 & 0.451 \\ 
leave-one-out\_sample\_crps & 0.331 & 0.348 & 0.314 \\ 
rolling window\_interval\_score & 0.448 & 0.519 & 0.464 \\ 
rolling window\_sample\_crps & 0.331 & 0.379 & 0.338 \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{4}{l}{horizon = 1} \\ 
\midrule\addlinespace[2.5pt]
expanding window\_interval\_score & 0.922 & 1.198 & 1.070 \\ 
expanding window\_sample\_crps & 0.709 & 0.882 & 0.828 \\ 
leave-one-out\_interval\_score & 0.902 & 1.187 & 1.051 \\ 
leave-one-out\_sample\_crps & 0.627 & 0.732 & 0.703 \\ 
rolling window\_interval\_score & 0.922 & 1.208 & 1.082 \\ 
rolling window\_sample\_crps & 0.720 & 0.906 & 0.854 \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{4}{l}{horizon = 1.5} \\ 
\midrule\addlinespace[2.5pt]
expanding window\_interval\_score & 1.163 & 1.424 & 1.271 \\ 
expanding window\_sample\_crps & 0.894 & 0.998 & 0.985 \\ 
leave-one-out\_interval\_score & 1.135 & 1.400 & 1.227 \\ 
leave-one-out\_sample\_crps & 0.765 & 0.855 & 0.838 \\ 
rolling window\_interval\_score & 1.170 & 1.431 & 1.270 \\ 
rolling window\_sample\_crps & 0.900 & 1.028 & 1.008 \\ 
\bottomrule
\end{longtable}

### 2024-08-28 manuscript/oecdactuals_bvarspecs.Rmd
old documentation (pre major manuscript)

wis_scores <- rbind(wis_scores, bvar_wis_scores) |>
    .d(source %in% c("IMF", "bvar_qu", "bvar_ciss"))
scores_cvgshort <- rbind(scores_cvgshort, bvar_scores_cvgshort)|>
    .d(source %in% c("imf", "bvar_qu", "bvar_ciss"))

@@

  dir_wis_plot <- wis_plot_new(decomp_data |> .d(error_method  == "directional"), trgt, xmax = xmax, plot_name = "WIS - Directional Errors", metcolor = "VanGogh2")
  abs_wis_plot <- wis_plot_new(decomp_data |> .d(error_method  == "absolute"), trgt, xmax = xmax, plot_name = "WIS - Absolute Errors", metcolor = "VanGogh2")

@@

  aeplot <- horizon_path_plot(point_scores |> .d(, error_method := "directional"), "meanae", "Absolute Error", title = "Point Forecast - Abs. Error")

  squeplot <- horizon_path_plot(point_scores |> .d(, error_method := "directional"), "meansque", "Squared Error", title = "Point Forecast - Squ. Error")

  crpsplot_rw <- horizon_path_plot(crps_scores_rw |>.d(, error_method := "directional"), "score", "CRPS by Sample", title = paste0("CRPS - ", window_method)) +
    scale_y_continuous(limits = c(0.07,1.05))

  crpsplot_loo <- horizon_path_plot(crps_scores_loo |>.d(, error_method := "directional"), "score", "CRPS by Sample", title = "CRPS - LOO") +
    scale_y_continuous(limits = c(0.07,1.05))

  ovr_plot <- 
    (abs_wis_plot) +
    plot_layout(guides = "collect", 
                heights = c(0.5, 0.5)) &
      plot_annotation(tag_levels = 'I')  &
      theme(legend.position = 'bottom', 
            legend.box="vertical", legend.margin=margin())

>>>>

wis_scores <- rbind(wis_scores, bvar_wis_scores) |>
    .d(source %in% c("IMF", "bvar_qu", "bvar_ciss"))
scores_cvgshort <- rbind(scores_cvgshort, bvar_scores_cvgshort)|>
    .d(source %in% c("imf", "bvar_qu", "bvar_ciss")) |>
  setnames("source", "model")

@@

  abs_wis_plot <- wis_plot_new(decomp_data |> .d(error_method  == "absolute"), trgt = trgt, xmax = xmax, plot_name = "WIS - Absolute Errors", metcolor = "VanGogh2")

@@

  ovr_plot <- 
    #(abs_wis_plot) +
    (c50plot / c80plot) +
    plot_layout(guides = "collect", 
                heights = c(0.5, 0.5)) &
      plot_annotation(tag_levels = 'I')  &
      theme(legend.position = 'bottom', 
            legend.box="vertical", legend.margin=margin())
